---
title: "Merging Data"
author: "Soki Kimura"
date: "2024-01-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Merging multiple imagery

Using the dataset for London from Landsat-8, I will join the 2 datasets together.


```{r load_libraries}

library(tidyverse)
library(terra)
library(fs)
library(here)
library(sf)
library(GLCMTextures)

```

```{r load_data}
# select first path
list1_path <- dir_info(here::here("data", "Landsat", "London_merge", "LC08_L2SP_201024_20230915_20230925_02_T1")) %>%
  dplyr::filter(str_detect(path, "[B1234567890].TIF")) %>%
  dplyr::select(path) %>%
  pull() %>%
  as.character()

# select second path
list2_path <- dir_info(here::here("data", "Landsat", "London_merge", "LC08_L2SP_202024_20231125_20231129_02_T1")) %>%
  dplyr::filter(str_detect(path, "[B1234567890].TIF")) %>%
  dplyr::select(path) %>%
  pull() %>%
  as.character()

# load data and reproject CRS
list1 <- terra::rast(list1_path) # UTM zone 31N (EPSG:32631)
list2 <- terra::rast(list2_path) # UTM zone 30N (EPSG:32630)

# list1_reproject <- list1 %>%
#   terra::project('EPSG:4326') 
# list2_reproject <- list2 %>%
#   terra::project('EPSG:4326')
```


The data come from different CRS (UTM zone 30N and 31N), so I reprojected one to the other, before creating the mosaic.

```{r reproject_data}

# reproject to the other one 
list1_reproject <- list1 %>%
  terra::project('EPSG:32630')

list1_resample <- list1_reproject %>%
  terra::resample(., list2)

# mosaic
m1 <- terra::mosaic(list1_resample, list2, fun = "mean")

list1
list1_reproject
list2

```

Plotting the results as follows:

```{r plot}
plot(m1)

# save as image
writeRaster(m1, here::here("data", "Landsat", "London_merge", "mosaic.tif"))

# view image
terra::plotRGB(
  m1,
  r = 4, g = 3, b = 2
)


```


```{r rename_layers}
# rename layers
names(m1) <- c("B1", "B2", "B3", "B4", "B5", "B6", "B7", "B10")
names(m1)

```

## Data Enhancements

### NDVI

Now, I will calculate the NDVI (Normalised Difference Vegetation Index) Index for this area .

The calculation is as follows:

$$
\text{NDVI} = \frac{\text{NIR}-\text{red}}{\text{NIR}+\text{red}}
$$

The NIR band is B5, and the red band is B4 in Landsat 8 imagery.

```{r NDVI}

m1_ndvi <-  (m1$B5 - m1$B4) / (m1$B5 + m1$B4)

plot(m1_ndvi)

```

### Subsetting the raster

In order to shorten the processing time, I will extract a single borough for the following analysis.

```{r mask_raster}

# get London Boroughs from London Datastore
boroughs <- st_read("https://data.london.gov.uk/download/london_boroughs/9502cdec-5df0-46e3-8aa1-2b5c5233a31f/London_Boroughs.gpkg")

# extract the London Borough of Camden
camden <- boroughs %>%
  dplyr::filter(name == "Camden") %>%
  st_transform(., 32630)

# crop using the geometry
m1_camden <- m1 %>%
  terra::crop(., camden) %>%
  terra::mask(., camden)

# save as image
writeRaster(m1_camden, here::here("data", "Landsat", "London_merge", "m1_camden.tif"))

```

### Texture

```{r texture}

scale <- (m1_camden * 0.0000275) - 0.2

# get texture
textures1 <- glcm_textures(
  scale$B4,
  # size of window
  w = c(7,7),
  # bins
  n_levels = 4,
  quantization = "equal range",
  shift = list(c(1, 0), c(1, 1), c(0, 1), c(-1, 1)),
  metrics = "glcm_homogeneity"
)

# plot
plot(textures1)

# save as image
writeRaster(textures1, here::here("data", "Landsat", "London_merge", "textures_camden.tif"))

```


I do not see much from this image here to be honest, maybe we should work wit hdata having better spatial resolution...

![Texture of Camden](data/Landsat/London_merge/textures_camden.tif)

### PCA

Let's do some dimensionality reduction for the dataset we have.

```{r PCA}

# combine the data
raster_and_texture <- c(m1_camden, textures1)

# run pca analysis
pca <- prcomp(
  as.data.frame(raster_and_texture, na.rm = TRUE),
  center = TRUE,
  scale = TRUE
)
summary(pca)

x <- predict(raster_and_texture, pca)

plot(x)

```


